Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\xavier{For the simulations shown below, we modelled a star similar to the Sun. The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on. The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets), and we use a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}. In addition, to be able to compare the result of those simulations with real data obtained with the HARPS spectrograph in Sect.~\ref{sec:4}, we asked SOAP 2.0 to generate CCFs of width 40 \kms and of resolution 115'000, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.}

>>>>

For the simulations discussed below, a star similar to the Sun was modeled. The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on. \jessi{The previous sentence seems incomplete and I'm not sure how to update it.}
The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?  Also, why is it referenced?  Is the effective temperature supposed to be similar to the Sun?}, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011} are used. 
In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms and a resolution of 115'000.  \jessi{Is a resolution of ``115'000'' standard notation?  I'm not sure what it means.}
%, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.
